Social Visual Analytics: DevOps for Data Scientists

### 2015-03-21 system.tex
i was working

\stephen{Let's work from front to back, from human interface to the
services and frameworks that support it.}

\stephen{I don't think we need to even make this argument, it seems so obvious.}
The internal computing infrastructure of organizations has changed
radically in the last fifteen years. The shift from large
servers toward scalable, lower-cost, distributed systems (``the cloud'')
led to a software ecosystem of processes distributed over a
network (often virtually defined) communicating via some
high-level protocol, usually HTTP. HTTP is dominant because web
browsers and servers are ubiquitous and available in almost
all hardware devices, from tiny sensors, to handheld devices and
laptops, to rack-mounted servers.

@@

The call mechanism is the URL itself; arguments are read from the URL
and the final cell is rendered as the result.  \stephen{That needs
more explanation.}

>>>>

% Stephen: Let's work from front to back, from human interface to the
% services and frameworks that support it.

The internal computing infrastructure of organizations has changed
radically in the last fifteen years. The shift from large
servers toward scalable, lower-cost, distributed systems (``the cloud'')
led to a software ecosystem of processes distributed over a
network, usually communicating via HTTP. HTTP is dominant because
web browsers and servers are ubiquitous and available in almost
all hardware devices, from tiny sensors, to handheld devices and
laptops, to rack-mounted servers.

@@

The call mechanism is the URL itself; arguments are read from the URL
and the final cell is rendered as the result.
